\documentclass[prd,12pt,nofootinbib]{revtex4}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{latexsym, amssymb}
\usepackage{verbatim}
\usepackage{lscape}
\usepackage{rotating}
\usepackage[export]{adjustbox}
\usepackage{subfloat}
%\usepackage{feynmp}
%\DeclareGraphicsRule{*}{mps}{*}{}

%  personal abbreviations and macros

\input{./mymacros.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% basic data for the eprint:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textwidth=6.0in  \textheight=8.25in

%%  Adjust these for your printer:
\oddsidemargin=+0.3in   \topmargin=-0.20in
\parskip=0.1truein

%% preprint number data:
%\newcommand\pubnumber{SLAC--PUB--16103}
%\newcommand\pubdate{\today}

%%  address and funding acknowledgement data:

%\def\Stanford{Pepperdine University,\\ 24255 Pacific Coast Hwy, Malibu, CA 90263, USA}
%\def\SLAC{SLAC National Accelerator Laboratory,\\ 2575 Sand Hill Road, Menlo Park, CA 94025, USA}
%\def\doeack{\footnote{Work supported by the US Department of Energy,
%                     contract DE--AC02--76SF00515.}}


\begin{document}

\begin{titlepage}
\title{Emergent Dimensions in Background Independent Quantum Gravity}
\author{Kassahun Betre$^{\dagger}$, Patrick Wells$^{\dagger}$}
\address{$^{\dagger}$Pepperdine University, 24255 Pacific Coast Hwy, Malibu, CA 90263, USA}

\maketitle

\begin{Abstract}
Abstract goes here.

\end{Abstract}

\end{titlepage}

\section{Introduction}
Background-independent models of spacetime geometry are increasingly common in the search for a quantum theory of gravity. If General Relativity is only an effective theory,  

Introduction \cite{Konopka:2008hp}, \cite{Chen:2012ui}, \cite{Konopka:2008ds}.
\section{Section 1}
\subsection{Evolution of the Model} 
Given an undirected, loopless graph $G$ with vertices $V(G) = \{ 1...N\}$ and edges $E(G)$, a Hamiltonian $H$ can be defined on the graph as follows:
\begin{equation}
H = J\sum_{i,j\in V(G), i\neq j}(d_i - d_j)^2 + K\sum_{v\in V(G)}d_v
\end{equation}
Where $J$ and $K$ are weighting constants, and $d_i$ simply represents the degree (number of connected edges) of a given node. The first of the sum forces the graph to be regular in the low-temperature limit, while the second sum pushes the graph to be more or less connected depending on the value of $K$. As $K$ goes to infinity, the expectation value of the average node degree drops to zero. Conversely, as $K$ tends towards negative infinity, the expectation value of the average node degree should go to $N-1$.
A set of seed graphs are evolved according to this Hamiltonian using a Monte-Carlo simulation with a Metropolis algorithm. 
\section{Geometrical Properties of Graphs}
Geometrical properties of the graphs considered are defined as in \cite{Knill:2011}. This definition of dimensionality is computationally problematic, not due to the complexity of the algorithm but rather due to its fundamentally recursive nature. Calculating the dimensionality of a complete graph $K_N$  on $N$ nodes requires $N!$ recursive calls, which quickly becomes computationally intractable as N increases. Of course, $K_N$ is just an N-1-dimensional simplex, but no such simplification exists for highly dense graphs close to $K_N$. While the graphs considered in the simulation were in general not so dense as to require such a high number of recursive calls, they were still complex enough to impose an upper limit on the size of the graphs considered.
\section{Conclusion}  
\begin{thebibliography}{99}
  


%\cite{Konopka:2008hp}
\bibitem{Konopka:2008hp} 
  T.~Konopka, F.~Markopoulou and S.~Severini,
  %``Quantum Graphity: A Model of emergent locality,''
  Phys.\ Rev.\ D {\bf 77}, 104029 (2008)
  doi:10.1103/PhysRevD.77.104029
  [arXiv:0801.0861 [hep-th]].
  %%CITATION = doi:10.1103/PhysRevD.77.104029;%%
  %92 citations counted in INSPIRE as of 24 May 2016

%\cite{Chen:2012ui}
\bibitem{Chen:2012ui} 
  S.~Chen and S.~S.~Plotkin,
  %``Statistical mechanics of graph models and their implications for emergent spacetime manifolds,''\cite{Chen:2012ui}
  Phys.\ Rev.\ D {\bf 87}, no. 8, 084011 (2013)
  doi:10.1103/PhysRevD.87.084011
  [arXiv:1210.3372 [gr-qc]].
  %%CITATION = doi:10.1103/PhysRevD.87.084011;%%
  %2 citations counted in INSPIRE as of 25 Aug 2016


%\cite{Konopka:2008ds}
\bibitem{Konopka:2008ds} 
  T.~Konopka,
  %``Statistical Mechanics of Graphity Models,''
  Phys.\ Rev.\ D {\bf 78}, 044032 (2008)
  doi:10.1103/PhysRevD.78.044032
  [arXiv:0805.2283 [hep-th]].
  %%CITATION = doi:10.1103/PhysRevD.78.044032;%%
  %24 citations counted in INSPIRE as of 24 Jun 2016

%\cite{Conrady:2010qz}
\bibitem{Conrady:2010qz} 
  F.~Conrady,
  %``Space as a low-temperature regime of graphs,''
  J.\ Statist.\ Phys.\  {\bf 142}, 898 (2011)
  doi:10.1007/s10955-011-0135-9
  [arXiv:1009.3195 [gr-qc]].
  %%CITATION = doi:10.1007/s10955-011-0135-9;%%
  %7 citations counted in INSPIRE as of 09 May 2018
  
  \bibitem{Knill:2011}
   O.~Knill
   %``On the Dimensionality and Euler Characteristic of Random Graphs``
   [arXiv:1112.5749 [math.PR]]
  
  
 
\end{thebibliography}




\end{document}
